---
title: "Writing R Packages I"
output:
  html_document: 
    toc: true
    toc_float: true
---


```{r, echo = FALSE}
knitr::opts_chunk$set(
  eval = FALSE,
  collapse = TRUE,
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

library(tidyverse)
library(rvest)

theme_set(theme_bw() + theme(legend.position = "bottom"))
```

Set seed for repoducibility
```{r}
set.seed(12345)
```


### Z score function

Z scores subtract the mean and divide by the sd
```{r}
x_vec = rnorm(20, mean = 5, sd = 0.3)
```

Compute z scores for x_vec
```{r}
(x_vec - mean(x_vec)) / sd(x_vec)
```


Write a function to do this:
```{r}
z_score = function(x) {
  
  if(!is.numeric(x)) {
    stop("Argument should be numbers")
  } else if (length(x) < 2) {
    stop("You need at least 2 numbers to get z-score")
  }
  
  z = x - mean(x) / sd(x)
  
  z
}
```

Check that this works:
```{r}
z_score(x = x_vec)
```

Keep checking:
```{r, error=TRUE}
z_score(x=3) #cannot take sd of one number

z_score(c(TRUE, TRUE, FALSE, TRUE)) # takes mean and sd of t/f converted to 1 and 0

z_score(iris) # doesn't know how to take mean and sd of an entire dataframe

```


### Multiple outputs

Write a function that returns the means and sd form a sample fo numbers
```{r}
mean_and_sd = function(x) {
  
    if(!is.numeric(x)) {
    stop("Argument should be numbers")
  } else if (length(x) < 2) {
    stop("You need at least 2 numbers to get z-score")
  }
  
  mean_x = mean(x)
  sd_x = sd(x)
  
  tibble(
    mean = mean_x,
    sd = sd_x
  )
}
```

Check if it works:
```{r}
mean_and_sd(x_vec)
```


### Start getting means and sds

```{r}

x_vec = rnorm(n = 30, mean = 5, sd = 0.5)

  tibble(
    mean = mean(x_vec),
    sd = sd(x_vec)
  )

# different sample is being generated every time this is ran
```


Write a function that uses `n`, a true mean, and true SD as inputs
```{r}
sim_mean_sd = function(n_obs, mu, sigma) {
  
  x_vec = rnorm(n = n_obs, mean = mu, sd = sigma)
  
  tibble(
    mean = mean(x_vec),
    sd = sd(x_vec)
  )  
}


sim_mean_sd(n_obs = 300, mu = 5, sigma = 0.5)

sim_mean_sd(12, 24, 4) 
```



### LOTR Dataset

```{r}

# what we did last time:
fellowship_ring = readxl::read_excel("./LotR_Words.xlsx", range = "B3:D6") |>
  mutate(movie = "fellowship_ring")


# function that does the same thing:
lotr_load_and_tidy = function(path = "./LotR_Words.xlsx", cell_range, movie_name) {
  
  movie_df = 
    readxl::read_excel(path, range = cell_range) |> 
    mutate(movie = movie_name) |> # can add more things inside function:
    janitor::clean_names() |> 
    pivot_longer(
      female:male,
      names_to = "sex",
      values_to = "words"
    )
  movie_df
}

# function in use
lort_df = 
  bind_rows(
    lotr_load_and_tidy(cell_range = "B3:D6", movie_name = "fellowship_ring"),
    lotr_load_and_tidy(cell_range = "F3:H6", movie_name = "two_towers"),
    lotr_load_and_tidy(cell_range = "J3:L6", movie_name = "return_king")
)
```



### NSDUH

```{r}
nsduh_url = "http://samhda.s3-us-gov-west-1.amazonaws.com/s3fs-public/field-uploads/2k15StateFiles/NSDUHsaeShortTermCHG2015.htm"

nsduh_html = read_html(nsduh_url)
```


function
```{r}
nsduh_import = function(html, table_number, outcome_name){
  
  html |> 
  html_table(table_number) |> 
  nth(1) |>
  slice(-1) |> 
  select(-contains("P Value")) |>
  pivot_longer(
    -State,
    names_to = "age_year", 
    values_to = "percent") |>
  separate(age_year, into = c("age", "year"), sep = "\\(") |>
  mutate(
    year = str_replace(year, "\\)", ""),
    percent = str_replace(percent, "[a-c]$", ""),
    percent = as.numeric(percent),
    outcome = outcome_name) |>
  filter(!(State %in% c("Total U.S.", "Northeast", "Midwest", "South", "West")))
}

#apply
nsduh_results = 
  bind_rows(
    nsduh_import(html = nsduh_html, table_number = 1, outcome_name = "marj"),
    nsduh_import(html = nsduh_html, table_number = 4, outcome_name = "cocaine"),
    nsduh_import(html = nsduh_html, table_number = 5, outcome_name = "heroin")
)
```










